%-------------------------------------------------------------------------------
\chapter{Guidelines}
\label{ch:guidelines}
%-------------------------------------------------------------------------------

This chapter provides general recommendations for writing a thesis for the Bachelor of Science in Artificial Intelligence. These guidelines are not meant to be prescriptive; they are just tips that give minimal guidance. You are the author of the thesis, and you have the final word about it.

\section{The Thesis}

The thesis must document a practical activity carried out as part of one of the labs offered by the Bachelor program or during a stage in a company. Considering the credits awarded for the thesis, it is reasonable to expect a 30 to 50-page document (all-inclusive).

A typical thesis includes
\begin{itemize}
    \item an introduction that summarizes the work;
    \item a presentation of the topic addressed (for instance, the description of a problem or the definition of a task);
    \item an analysis of the relevant literature for that topic and a summary of the most important state-of-the-art solutions;
    \item a description of the main contribution of the thesis;
    \item a report of the results obtained;
    \item conclusions reviewing the main points;
    \item the list of bibliographic references cited in the thesis.
\end{itemize}
%
These can be presented as separate chapters or sections of chapters covering multiple points. 

\section{The Advisor}

You will write the thesis under the supervision of an advisor who will give you directions and advice. Regular meetings with your advisor are strongly recommended during thesis preparation. When you have a draft of a chapter, please send it to them for revision. Leave a reasonable time for the revision (e.g., one week per chapter); otherwise, the advisor may be forced to delay your graduation to the following session. 

The advisor \textbf{is not} supposed to proofread the text. Please ensure the text is written in clear and correct English before submitting it for revision.

\section{General Advice}

The goal of writing a thesis is to document your work in a way that can be evaluated by others. Be explicit in what is your personal contribution, and if adequate, make sure to present the challenges encountered and the ideas generated.

There are no extra points for being prolific. You should be clear, precise, and concise. A good advice is to write everything that you think that is necessary, and then \textbf{stop}. Then go back and get rid of things that were not really necessary.

Remember that writing is difficult and takes time. Most students underestimate the effort required to produce a good manuscript. Please take this into account. You are finishing a 3-year course on AI, and surely know about generative AI tools. If you are planning to use these for writing your thesis, check first what is the official policy from the programme and, in any case, use them only as \textbf{aids}. You should be aware of all the limitations and drawbacks of these methods and you (and only you) are responsible for what is written in your thesis.